Implementation of Concurrent Hash Tables in Java

### 2022-04-29 paper.tex
Code for put()

\section{Algorithms}
There are many ways to create single-threaded hash tables, so there are likewise many ways to create concurrent hash tables. If we ignore the need for resizing and
the choice of hashing algorithm, we still need to decide on an approach for handling contention. We will attempt to employ methods such as course-grain locking, fine-grain locking,
lazy, optimistic, and lock-free design.

\section{Experimental Results}
We begin by testing how the standard hash table will performed when run sequentially, and then when multithreaded.

>>>>

\section{Algorithms}
\subsection{Basic Hashtable}
\begin{lstlisting}[language={Java},caption=Source code for the course-grain put() method.,captionpos=b,breaklines=true,frame=single]
public synchronized boolean put(int item) {
    // If capacity if full, do not add
    if (capacity >= ARR_SIZE)
        return false;

    // Get key
    int key = hash(item);

    // Check if first try addition
    if (table[key] == null) {
        table[key] = item;
        cleans[key] = false;
    }
    // Otherwise, quadratically probe for empty indices
    else {
        int i = 1;
        int new_key = (key + i) % ARR_SIZE;
        while (table[new_key] != null) {
            i++;
            new_key = (new_key + i) % ARR_SIZE;
        }
        table[new_key] = item;
        cleans[new_key] = false;
    }

    // Increase capacity
    capacity++;
    return true;
}
\end{lstlisting}
\section{Experimental Results}
We begin by testing how the standard hash table will performed when run sequentially, and then when multithreaded.
